Progress Report

### 2018-11-27 main.tex
formatting
dunno
no big files

\documentclass{article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{natbib}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{lineno}
\usepackage{color}
\usepackage{auto-pst-pdf}
\usepackage[colaction]{multicol}
\usepackage{caption}
\usepackage{svg}

@@

 		{\large\textbf{\@author}}
	\end{flushleft}\egroup
}
\makeatother

@@

% Title
\title{A Topic Model of Climate Change Literature}
\title{Words, words, words: Mapping the Matter of Climate Change Literature}
\title{A Topography of Climate Change Research}
\author{Max Callaghan}

@@

Various researchers have attempted to do empirical research on the assessment reports, and processes of inter. alia. the IPCC \citep{jabbour2017} \citep{Bjurström2011} \citep{Hulme2016}.

@@

>>>>

<<<<<<< HEAD
\documentclass{article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{natbib}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{lineno}
\usepackage{color}
%\usepackage{auto-pst-pdf}
\usepackage[colaction]{multicol}
\usepackage{caption}
\usepackage{svg}
\usepackage{authblk}

@@

 		{\large\textbf{\@author}}

 		{\large{Draft current \@date}}

	\end{flushleft}\egroup
}
\makeatother

@@

% Title
\title{A Topic Model of Climate Change Literature}
\title{Words, words, words: Mapping the Matter of Climate Change Literature}
\title{A Topography of Climate Change Research}
\author[1,2]{Max Callaghan}

\affil[1]{Mercator Research Institute on Global Commons and Climate Change, Torgauer Straße, 10829 Berlin, Germany}
\affil[2]{School of Earth and Environment, University of Leeds, Leeds LS2 9JT, United Kingdom}

@@

Various researchers have attempted to do empirical research on the assessment reports, and processes of inter. alia. the IPCC \citep{jabbour2017} \citep{Bjurström2011} \citep{Corbera2016} \citep{Hulme2016}.

\begin{table}
	\scriptsize	
	\input{tables/growth_table.tex}
	\caption{Growth in climate change literature}
\end{table}

%\begin{figure}
%	\begin{center}
%		\includegraphics[width=0.5\linewidth]{plots/literature_size/volume_variety.pdf}
%		%\captionof{figure}
%		\caption{The volume and variety of literature on climate change has grown to unmanageable proportions. Each box represents a document-term matrix (unique documents x unique terms) of the abstracts written in each assessment period. The percentage of documents in which the average word occurs in is given in the key.
%		}
%		\label{growth}
%	\end{center}
%\end{figure}

\begin{table}
	\scriptsize	
	\input{tables/top_topics.tex}
	\caption{Top 10 topics in climate change literature}
\end{table}

\begin{figure}
	\begin{center}
		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_double.pdf}
		\caption{A map of the literature on climate change. Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by working group citations (top) and web of science discipline category (bottom). See SI table for further description}
		\label{}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_evolution.pdf}
		\caption{The evolution of the landscape of climate change literature}
		\label{}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
		%\includegraphics[width=1\linewidth]{plots/network_development_wgs_665.pdf}
		\caption{The development of the topic-document correlation network over IPCC assessment periods.}
		\label{}
	\end{center}
\end{figure}

=======
\documentclass{article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{natbib}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{lineno}
\usepackage{color}
\usepackage{auto-pst-pdf}
\usepackage[colaction]{multicol}
\usepackage{caption}
\usepackage{svg}
\usepackage{authblk}

 		{\large\textbf{\@author}}

 		{\large{Draft current \@date}}

	\end{flushleft}\egroup
}
\makeatother

% Title
\title{A Topic Model of Climate Change Literature}
\title{Words, words, words: Mapping the Matter of Climate Change Literature}
\title{A Topography of Climate Change Research}
\author[1,2]{Max Callaghan}

\affil[1]{Mercator Research Institute on Global Commons and Climate Change, Torgauer Straße, 10829 Berlin, Germany}
\affil[2]{School of Earth and Environment, University of Leeds, Leeds LS2 9JT, United Kingdom}

Various researchers have attempted to do empirical research on the assessment reports, and processes of inter. alia. the IPCC \citep{jabbour2017} \citep{Bjurström2011} \citep{Corbera2016} \citep{Hulme2016}.

@@

>>>>>>> 0261e7b8054b72195fb991f1ca7947fd5b9a6b9d

### 2018-11-27 prog_report.tex
no big files

<<<<<<< HEAD
\documentclass{article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{natbib}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{lineno}
\usepackage{color}
%\usepackage{auto-pst-pdf}
\usepackage[colaction]{multicol}
\usepackage{caption}
\usepackage{svg}
\usepackage{authblk}

@@

 		{\large{Draft current \@date}}

@@

\newcommand{\multicollinenumbers}{
	\linenumbers
	\def\makeLineNumber{\docolaction
		{\makeLineNumberLeft}
		{}
		{\makeLineNumberRight}
		}
}

\newenvironment{figurehere}
	{\def\@captype{figure}}
	{}

% Title
\title{A Topic Model of Climate Change Literature}
\title{Words, words, words: Mapping the Matter of Climate Change Literature}
\title{A Topography of Climate Change Research}
\author[1,2]{Max Callaghan}

\affil[1]{Mercator Research Institute on Global Commons and Climate Change, Torgauer Straße, 10829 Berlin, Germany}
\affil[2]{School of Earth and Environment, University of Leeds, Leeds LS2 9JT, United Kingdom}

@@

\begin{linenumbers}

\begin{table}
	\scriptsize	
	\input{tables/growth_table.tex}
	\caption{Growth in climate change literature}
\end{table}

%\begin{figure}
%	\begin{center}
%		\includegraphics[width=0.5\linewidth]{plots/literature_size/volume_variety.pdf}
%		%\captionof{figure}
%		\caption{The volume and variety of literature on climate change has grown to unmanageable proportions. Each box represents a document-term matrix (unique documents x unique terms) of the abstracts written in each assessment period. The percentage of documents in which the average word occurs in is given in the key.
%		}
%		\label{growth}
%	\end{center}
%\end{figure}

\begin{table}
	\scriptsize	
	\input{tables/top_topics.tex}
	\caption{Top 10 topics in climate change literature}
\end{table}

\begin{figure}
	\begin{center}
		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_double.pdf}
		\caption{A map of the literature on climate change. Document positions are obtained by reducing the topic scores to two dimensions via t-SNE Documents are coloured by working group citations (top) and web of science discipline category (bottom). See SI table for further description}
		\label{}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
		%\includegraphics[width=1\linewidth]{tsne_results/plots/run_665_s_0_p200_evolution.pdf}
		\caption{The evolution of the landscape of climate change literature}
		\label{}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
		%\includegraphics[width=1\linewidth]{plots/network_development_wgs_665.pdf}
		\caption{The development of the topic-document correlation network over IPCC assessment periods.}
		\label{}
	\end{center}
\end{figure}

%Increase in the frequency of the use of the term ``solutions'' \citep{jabbour2017},

\section*{Methods}
\label{methods}

\subsection*{Data}
%This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on Web of Science. Though not exhaustive, it gives a good coverage of

\end{linenumbers}

%\end{multicols}

\listoffigures
\linespread{1}
\bibliography{Mendeley.bib}
\bibliographystyle{unsrt}

=======
\documentclass{article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{natbib}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{lineno}
\usepackage{color}
\usepackage{auto-pst-pdf}
\usepackage[colaction]{multicol}
\usepackage{caption}
\usepackage{svg}
\usepackage{authblk}

 		{\large{Draft current \@date}}

\newcommand{\multicollinenumbers}{
	\linenumbers
	\def\makeLineNumber{\docolaction
		{\makeLineNumberLeft}
		{}
		{\makeLineNumberRight}
		}
}

\newenvironment{figurehere}
	{\def\@captype{figure}}
	{}

% Title
\title{A Topic Model of Climate Change Literature}
\title{Words, words, words: Mapping the Matter of Climate Change Literature}
\title{A Topography of Climate Change Research}
\author[1,2]{Max Callaghan}

\affil[1]{Mercator Research Institute on Global Commons and Climate Change, Torgauer Straße, 10829 Berlin, Germany}
\affil[2]{School of Earth and Environment, University of Leeds, Leeds LS2 9JT, United Kingdom}

\begin{linenumbers}

@@

\begin{figure}
	\begin{center}
		\includegraphics[width=1\linewidth]{plots/tsne.png}
		\caption{A map of a sample of 10,000 documents about climate change. Document positions are obtained by reducing the topic scores to two dimensions via t-SNE}
		\label{}
	\end{center}
\end{figure}

@@

%Increase in the frequency of the use of the term ``solutions'' \citep{jabbour2017},

\section*{Methods}
\label{methods}

\subsection*{Data}
%This study reproduces the query developed by \citep{Grieneisen2011}, which is carried out on Web of Science. Though not exhaustive, it gives a good coverage of

\end{linenumbers}

%\end{multicols}

\listoffigures
\linespread{1}
\bibliography{Mendeley.bib}
\bibliographystyle{unsrt}

@@

>>>>>>> 0261e7b8054b72195fb991f1ca7947fd5b9a6b9d

>>>>

\documentclass{article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{natbib}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{lineno}
\usepackage{color}
\usepackage{caption}
\usepackage{svg}
\usepackage{authblk}
\usepackage{hyperref}
\hypersetup{
	pdfinfo={
		Author={Max Callaghan},
		Title={Progress Report},
		CreationDate={D:20180601195600},
		ModDate={...},
		Keywords={PDF;LaTeX},
	}
}

@@

		{\large\textbf{\@date}}

@@

% Title
\title{Progress Report}
\author{Max Callaghan}
\date{1 June 2016}

@@

\section{Overview}

The majority of my work in 2018 has been focussed on what will be my first first-authored publication, \textit{A Topography of Climate Change Literature}. A working draft of the introduction and some preliminary results are included in section 2, Paragraph headings are given in bold, with full paragraphs below sometimes to be flushed out. In parallel to this, and in support of the analysis, I have been further developing the tools documented in \url{https://github.com/mcallaghan/tmv} and described in section 3.1. These have further supported, and been improved by ideas generated from the collaborative work detailed in section 3.2. Section 3.3 elucidates other ideas for papers which will directly support my PhD.

%\begin{figure}
%	\begin{center}
%		\includegraphics[width=0.9\linewidth]{/home/max/Documents/admin/leeds/candidature_report/max_18_pr.png}
%		%\captionof{figure}
%		\caption{
%		}
%		\label{activity}
%	\end{center}
%\end{figure}
%
%As a large part of my work is recorded in online repositories, figure \ref{activity} gives an overview to the time resources I have committed to each project recorded on Github.

\section{A Topography of Climate Change Literature}

@@

%\begin{figure}
%	\begin{center}
%		\includegraphics[width=1\linewidth]{plots/tsne.png}
%		\caption{A map of a sample of 10,000 documents about climate change. Document positions are obtained by reducing the topic scores to two dimensions via t-SNE}
%		\label{}
%	\end{center}
%\end{figure}

@@

\section{Other Projects}

\subsection{Tools}
The architecture of tools included in the TMV repository has expanded. The repository was built originally to view topic models interactively,  then extended to manage queries and systematic reviews. The query management part has facilitated the systematic reviews on negative emissions technologies (NETs) recently published. The joining together of the query management and topic model viewing parts of the tool through an interface to run topic models on queries has allowed for wider use. Planned additions include a system to record estimates for a meta-analysis, and the incorporation of machine-learning to speed up the screening process.

\subsection{Co-authored papers}

\subsubsection{Submitted}

\citep{Lamb2018a} lays out a new role for machine-reading in evidence synthesis and as such is highly relevant to my PhD. 
through the provision of the infrastructure to model topics, the iteration of models to choose the right topic size, the editing of the manuscript and the provision of data for the creation of figures.

\citep{Hilaire2018} synthesises evidence from integrated assessment models on NETs by collecting and classifying statements about NETs. Together with first author Jérôme Hilaire, I added new functionality to the query management tool to provide for the classification of text excerpts from PDFs, and classified a portion of the statements.

\subsubsection{Published}

I contributed to \citep{Lamb2018} through the provision of the infrastructure to model topics, the iteration of models to choose the right topic size, the editing of the manuscript and the provision of data for the creation of figures.

\citep{Minx2018}, \citep{Fuss2018} and \citep{Nemet2018}. Form a highly ambitious systematic review on negative emissions technologies. The query management tool contributed to the efficient and accurate screening of papers across a geographically dispersed team and the management of publication data. I further contributed to the review's analysis by creating the heat bars in \citep{Fuss2018}.

\subsection{Paper ideas}

\subsubsection{Rapid Systematic Maps}
This paper should lay out, and validate the methods used in \citep{Lamb2018a}. The use of topic modelling to produce systematic maps is innovative: this paper should explain the methods and validate results against a human-coded dataset.

\subsubsection{Quantifying the science-policy interface}
In this paper, I aim, with scientometrics, to measure the properties of the knowledge pyramid, conceptualised by theorists of the science-policy interface. What kind of, and how many publications make up each layer of the pyramid, and how does information flow between layers?

\linespread{1}
\bibliography{Mendeley.bib}
\bibliographystyle{unsrt}

@@
